Co-methylation review

### 2014-12-21 Rmarkdown/comethylation_review.Rmd
Updated coMET reference

The `coMET` `R` package ([http://epigen.kcl.ac.uk/comet/](http://epigen.kcl.ac.uk/comet/)) can be used to estimate and plot between-sample co-methylation heatmaps from Illumina HumanMethylation450 array data. However, it is as yet unpublished and is still  in development at the time of writing.

>>>>

A simple way to estimate between-sample co-methylation is to create a matrix of $\beta$-values, $\bm{\beta}$, where the $(i, j)$ entry is $\beta_{i, j}$. Then, compute $R = cor(X^{T})$, whose $(k, l)$ entry is $cor(\bm{\beta_{., k}}, \bm{\beta_{., l}})$, where $\bm{\beta_{., k}}$ is the column vector of $\beta$-values for the $k^{th}$ methylation loci. This is what the R package, `coMET`   ([http://bioconductor.org/packages/devel/bioc/html/coMET.html](http://bioconductor.org/packages/devel/bioc/html/coMET.html)), does to estimate the between-sample co-methylation of Illumina HumanMethylation450 array data.
